OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-06-07 main.tex
Fixing Figures 1 and 6 legends

\begin{figure}
\centerline{\includegraphics[width=.45\textwidth]{img/figure1.pdf}}
\caption{Total amount of contacts per bin. A. Non linear relationship
between the number of restriction sites and the total number of
contacts per bin in T47D. B. Total number of contacts per bin on
chromosome 17 of T47D. Raw (brown) and corrected (blue) signals are shown.
The long arm of chromosome 17 (the region corresponding to 20-40 Mbp) is
present in four coipes, explaining that the signal is about twice higher
than for the short arm.}
\label{fig:totals}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=.5\textwidth]
  {img/figure_cnv_correction.pdf}}
\caption{
Copy number correction A. Detail of a Hi-C matrix normalized with
different methods. The central portion has an increased copy number, which
affects normalization. \textit{ICE} fades it away, \textit{LGF} enhances
it and \textit{OneD} reduces the signal by about half. B. Profile of the
total amount of contacts after copy numer correction. The plot shows the
same region as Figure\ref{fig:totals}B. The brown line represents the raw
signal, the blue line represents the signal after bias correction, the
black line represents the signal after bias and copy number correction.}
\label{fig:cnv_correction}
\end{figure}

@@

This work was supported by the Spanish Ministry of Economy and
Competitiveness, ‘Centro de Excelencia Severo Ochoa 2013-2017’,
SEV-2012-0208, ERC Synergy Grant 609989 and...

>>>>

\begin{figure}
\centerline{\includegraphics[width=.45\textwidth]{img/figure1.pdf}}
\caption{Total amount of contacts per bin. A. Non linear relationship
between the number of restriction sites and the total number of
contacts per bin in T47D. B. Total number of contacts per bin on
chromosome 17 of T47D. The brown line represents the raw
signal, the blue line represents the signal after bias correction, the
black line represents the signal after bias and copy number correction.
The long arm of chromosome 17 (the region corresponding to 20-80 Mbp) is
present in four copies, explaining that the signal is about twice higher
than for the short arm.}
\label{fig:totals}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=.5\textwidth]
  {img/figure_cnv_correction.pdf}}
\caption{
Copy number correction A. Detail of a Hi-C matrix normalized with
different methods. The central portion has an increased copy number, which
affects normalization. \textit{ICE} fades it away, \textit{LGF} enhances
it and \textit{OneD} reduces the signal by about half. B. Profile of the
total amount of contacts after copy numer correction. The plot shows the
same region as panel A. The brown line represents the raw
signal, the blue line represents the signal after bias correction, the
black line represents the signal after bias and copy number correction.}
\label{fig:cnv_correction}
\end{figure}

@@

This work was supported by the Spanish Ministry of Economy and
Competitiveness, ‘Centro de Excelencia Severo Ochoa 2013-2017’,
SEV-2012-0208 and ERC Synergy Grant 609989. R.S. was supported by an EMBO Long-term
Fellowship (ALTF 1201-2014) and a Marie Curie Individual Fellowship (H2020-MSCA-IF-2014).
